% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Evan M. Herrnstadt}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://www.evanherrnstadt.com/docs/HerrnstadtCV_current.pdf/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large \textbf}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \vspace{-0.5em}
  \begin{list}{}{
	\itemsep=0em
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


\begin{document}

% Place name at left
{\Large \textbf\name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.cbo.gov/}{Congressional Budget Office} \\
  Ford House Office Building \\
  2nd and D St. SW \\
  Washington, DC 20515
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:Evan.Herrnstadt@cbo.gov}{\tt Evan.Herrnstadt@cbo.gov} \\
    Homepage: & \href{http://www.evanherrnstadt.com/}{\tt http://www.evanherrnstadt.com/} \\
    Citizenship: & United States \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
  \item Ph.D., Economics, University of Michigan \hfill 2015
  \item M.A., Economics, University of Michigan \hfill 2011
  \item B.S., Economics (honors) and Political Science, University of Iowa \hfill 2006
\end{itemize}


\section*{Employment}
\begin{itemize}
\item Principal Analyst, Microeconomic Studies Division, Congressional Budget Office \hfill 2021--Present
\item Associate Analyst, Microeconomic Studies Division, Congressional Budget Office \hfill 2019--2021
\item Vice President, Compass Lexecon \hfill 2019
\item Senior Economist, Compass Lexecon \hfill  2017--2019
\item Kernan Brothers Environmental Fellow, Harvard University \hfill 2015--2017
\end{itemize}


\section*{Publications}

\begin{itemize}
\item Herrnstadt, Evan and Richard Sweeney, “Housing Market Capitalization of Pipeline Risk: Evidence from the San Bruno Explosion,” Forthcoming at \emph{Land Economics}.

\item Staff of the Congressional Budget Office (Contributor), "How Economists Could Help Inform Economic and Budget Analysis Used by the US Congress", 
\textit{Journal of Economic Perspectives}, 38 (Spring 2024), p. 3-24.
	
\item Herrnstadt, Evan, Ryan Kellogg, and Eric Lewis. “Royalties and Deadlines in Oil and Gas Leasing: Theory and Evidence”, \textit{Econometrica}, 92 (Jan. 2024), 29-60.

\item Herrnstadt, Evan, Anthony Heyes, Erich Muehlegger, and Soodeh Saberian. “Air Pollution and Criminal Activity: Microgeographic Evidence from Chicago”, \textit{American Economic Journal: Applied Economics}, 13 (Oct. 2021), 70-100.

\item Herrnstadt, Evan, Ian Parry, and Juha Siikamäki. “Do alcohol taxes in Europe and the US rightly correct for externalities?” \textit{International Tax and Public Finance}, 22 (Feb. 2015), 73-101.

\item Herrnstadt, Evan, and Erich Muehlegger.  “Weather, Salience of Climate Change, and Congressional Voting.” \textit{Journal of Environmental Economics and Management}, 68 (Nov. 2014), 435-448.

\item Fischer, Carolyn, Evan Herrnstadt, and Richard Morgenstern. “Understanding Errors in EIA Projections of Energy Demand.”  \textit{Resource and Energy Economics}, 30 (Aug. 2009), 198-209.
\end{itemize}

\section*{Working Papers}

\begin{itemize}
\item “Conservation Versus Competition? Environmental Objectives in Government Contracting” 

\end{itemize}

\section*{Congressional Budget Office Products}
\begin{itemize}
\item "Greenhouse Gas Emissions in the Manufacturing Sector" (with Austin Castellanos), 2024.
\item "Flood Damage and Federally Backed Mortgages in a Changing Climate" (with Jeffrey Perry), 2023.
\item "How CBO Analyzes the Effects of Charging the Oil and Gas Industry for Methane Emissions" (with Austin Castellanos), 2022.
\item "Technical Information About How CBO Models the Effects of Climate Change on Output in Its Long-Term Economic Projections", 2021.
\item "CBO’s Model of Drug Price Negotiations Under the Elijah E. Cummings Lower Drug Costs Now Act" (with Chris Adams), CBO Working Paper 2021-01
\item "CBO’s Estimate of the Effects of Climate Change on U.S. Economic Output" (with Terry Dinan), CBO Working Paper 2020-06
\item Cost Estimate for S. 2881, 5G Spectrum Act
\item Cost Estimate for H.R. 3, Elijah E. Cummings Lower Drug Costs Now Act
\end{itemize}

\section*{Consulting Casework}
\begin{itemize}
\item \textbf{Completed merger of AT\&T and Time Warner}
\begin{itemize}
\item Supported experts Dennis Carlton and Michael Katz on behalf of the defendants in \textit{United States of America vs. AT\&T, Inc. et al.}
\end{itemize}
\item \textbf{Completed merger of T-Mobile and Sprint}
\begin{itemize}
\item Supported experts Mark Israel, Michael Katz, and Bryan Keating on behalf of the merging parties.
\end{itemize}
\end{itemize}

\section*{Awards and Fellowships}
\begin{itemize}
\item CBO Director's Award \hfill 2021
\item Joseph L. Fisher Dissertation Fellowship, Resources for the Future	\hfill 2014
\item Phi Beta Kappa, Alpha of Iowa Chapter	\hfill 2006
\end{itemize}

\section*{Selected Presentations}
\begin{itemize}
	\item 2018-19: Resources for the Future
	\item 2017-18: University of Pennsylvania (Wharton/Kleinman Center for Energy Policy)
	\item 2016-17: Harvard Kennedy School, University of Michigan
	\item 2015-16: AEA Annual Meetings, AERE Summer Conference, University of Illinois Heartland Workshop
	\item 2014-15: NBER Hydrocarbon Infrastructure and Transport, NBER SI EEE (sketch), Resources for the Future
\end{itemize}

\section*{Professional Activities}
\begin{itemize}
\item Referee for AEJ:Policy, JEEM, JAERE, Nature Energy
\end{itemize}


\end{document}
